---
title: "MOVIES DATABASE"
author: "Chester Poon"
date: "9/7/2018"
output: html_document
---

Data collection for this assignment was a bit tricky.  Though it was clear that the data need not be totally valid for this assignment, I felt the need to at least try to get accurate data.  Since most people watch completely different movies at different times, it was hard to find 6 movies that people had commonly watched.  So I pulled the top grossing films of 2017 and 2018 and gathered the scoring results from 6 people and 1 dog.  Respondents scored on a scale from 1 to 5; 5 being excellent, 1 being terrible.  If a respondent did not see a movie, no score was given.

First we load the data into the database (see SQL script) and now we build a connection to the server with R.

```{r}
library(RMySQL)

movie_connect <- dbConnect(MySQL(),
                           user = 'root',
                           password = '',
                           host = 'localhost',
                           dbname = 'movies')

summary(movie_connect)
```

Now that we have a connection to the database, let's run a simple query to get how people scored each movie that they saw.

```{r}
dbGetQuery(movie_connect, 
"
SELECT
	P.NAME
  ,M.MOVIE
  ,S.SCORE
FROM SCORE S
  INNER JOIN PERSON P ON S.NAME_ID = P.NAME_ID
  INNER JOIN MOVIES M ON S.MOVIE_ID = M.MOVIE_ID;
")
```

This just returns a basic raw data set.  Just for fun, let's take a deeper dive into the most watched films from this small group of people.  

```{r}
dbGetQuery(movie_connect, 
"
SELECT
  M.MOVIE
  ,COUNT(DISTINCT S.SCORE_ID) AS COUNT
FROM SCORE S
  INNER JOIN MOVIES M ON S.MOVIE_ID = M.MOVIE_ID
GROUP BY
  M.MOVIE
ORDER BY
  COUNT(DISTINCT S.SCORE_ID) DESC
;
")
```

Looks like the most watched films are Black Panther, Star Wars, Wonder Woman, and Beauty and the Beast.  Let's create a simple visualization that depicts the average score across these four movies.  We'll also alter the SQL query so that if we ever update the data and anything changes, we can always pull the top four movies that have been scored in our database.

```{r}
library(ggplot2)

TOP4 <- dbGetQuery(movie_connect, 
"
SELECT
  MOV.MOVIE
  ,AVG(S.SCORE) AS AVG_SCORE
FROM SCORE S
  INNER JOIN (
      SELECT
        M.MOVIE
        ,M.MOVIE_ID
        ,COUNT(DISTINCT S.SCORE_ID) AS COUNT
      FROM SCORE S
        INNER JOIN MOVIES M ON S.MOVIE_ID = M.MOVIE_ID
      GROUP BY
        M.MOVIE
        ,M.MOVIE_ID
      ORDER BY
        COUNT(DISTINCT S.SCORE_ID) DESC
      LIMIT 4
  ) MOV ON S.MOVIE_ID = MOV.MOVIE_ID

GROUP BY
  MOV.MOVIE
ORDER BY
  AVG(S.SCORE) DESC
;
")

ggplot(TOP4, aes(x = MOVIE ,y = AVG_SCORE, fill = MOVIE)) +
  geom_col() +
  theme(axis.text.x = element_text(face="bold", angle=45, hjust = 1))
```

