---
title: "MOVIES DATABASE"
author: "Chester Poon"
date: "9/7/2018"
output: html_document
---

Data collection for this assignment was a bit tricky.  Thought it was clear that the data need not be totally valid for this assignment, I felt the need to at least try to get accurate data.  Since most people watch completely different movies at different times, it was hard to find 6 movies that people had commonly watched.  So I pulled the top grossing films of 2017 and 2018 and gathered the scoring results from 6 people and 1 dog.

First we load the data into the database (see SQL script) and now we build a connection to the server with R.

```{r}
library(RMySQL)

movie_connect <- dbConnect(MySQL(),
                           user = 'root',
                           password = '*******',
                           host = 'localhost',
                           dbname = 'movies')

summary(movie_connect)
```

Now that we have a connection to the database, let's run a simple query to get what people scored each movie that they saw.

```{r}
dbGetQuery(movie_connect, 
"
SELECT
	P.NAME
  ,M.MOVIE
  ,S.SCORE
FROM SCORE S
  INNER JOIN PERSON P ON S.NAME_ID = P.NAME_ID
  INNER JOIN MOVIES M ON S.MOVIE_ID = M.MOVIE_ID;
")
```

Kind of boring to look at.  Just for fun, let's take a deeper dive into the most watched films from this small group of people.  

```{r}
dbGetQuery(movie_connect, 
"
SELECT
  M.MOVIE
  ,COUNT(DISTINCT S.SCORE_ID) AS COUNT
FROM SCORE S
  INNER JOIN MOVIES M ON S.MOVIE_ID = M.MOVIE_ID
GROUP BY
  M.MOVIE
ORDER BY
  COUNT(DISTINCT S.SCORE_ID) DESC
;
")
```

Looks like the most watched films are Black Panther, Star Wars, Wonder Woman, and Beauty and the Beast.  Let's create a simple visualization that depicts the average score across these four movies.

```{r}
library(ggplot2)

TOP4 <- dbGetQuery(movie_connect, 
"
SELECT
  M.MOVIE
  ,AVG(S.SCORE) AS AVG_SCORE
FROM SCORE S
  INNER JOIN MOVIES M ON S.MOVIE_ID = M.MOVIE_ID
    AND M.MOVIE_ID IN ('BLA','STA','WON','BEA')
GROUP BY
  M.MOVIE
ORDER BY
  AVG(S.SCORE) DESC
;
")

ggplot(TOP4, aes(x = MOVIE ,y = AVG_SCORE, fill = MOVIE)) +
  geom_col() +
  theme(axis.text.x = element_text(face="bold", angle=45, hjust = 1))
```

